---
title: "Gut_RTD"
author: "Emmi Mueller"
date: "2/7/2020"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
getwd()
require("sfsmisc")
require("ggplot2")
require("ggpmisc")
require("ggpubr")
require("cowplot")
require("bbmle")
require("ggpubr")
require("igraph")
```
## Including Plots

```{r figure_setup}
my.cols <- RColorBrewer::brewer.pal(n = 4, name = "Greys")[3:4]

# Set theme for figures in the paper
theme_set(theme_classic() + 
  theme(axis.title = element_text(size = 20),
        axis.title.x = element_text(margin = margin(t = 15, b = 15)),
        axis.title.y = element_text(margin = margin(l = 15, r = 15)),
        axis.text = element_text(size = 15),
        axis.text.x = element_text(margin = margin(t = 5)),
        axis.text.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.x = element_line(size = 1),
        axis.ticks.y = element_line(size = 1),
        axis.ticks.length = unit(.1, "in"),
        plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15),
        strip.text = element_text(size = 20),
        strip.background = element_blank()
        ))
```

```{r}
CDF <- function(data){
  x <- data[1,"E"]
  y <- 1
  while( y < length(data$E)){
    x <- c(x, x[length(x)] + data[y, "E"])
    y <- y + 1
  }
  return(x)
}

RTD <- function(X){
  X <- X[7:66,]
  X$E <- X$Conc/(integrate.xy(X$Time, X$Conc, a = 3, b= 32.5))
  X[3,"E"]
  f <- X[3,"E"]
  x <- 3.5
  while (x < 33){
    f <- c(f, integrate.xy(X$Time, X$E, a = 3, b= x))
    x <-  x + 0.5
  }
  X$f <- f
  return(X)
}
```


#Load data and determine medians by hand with numerical integration
```{r}
NV_20200212_25 <- read.csv("../data/RTD/20200212_NV_RTD.csv", header = TRUE, sep = ",")
NV_20200212_25 <- RTD(NV_20200212_25)

NV_20200218_25 <- read.csv("../data/RTD/20200218_NV_RTD.csv", header = TRUE, sep = ",")
NV_20200218_25 <- RTD(NV_20200218_25)

NV_20200211_14 <- read.csv("../data/RTD/20200211_NV_RTD.csv", header = TRUE, sep = ",")
NV_20200211_14 <- RTD(NV_20200211_14)

NV_20200219_14 <- read.csv("../data/RTD/20200219_NV_RTD.csv", header = TRUE, sep = ",")
NV_20200219_14 <- RTD(NV_20200219_14)

HV_20200218_25 <- read.csv("../data/RTD/20200218_HV_RTD.csv", header = TRUE, sep = ",")
HV_20200218_25 <- RTD(HV_20200218_25)

HV_20200212_25 <- read.csv("../data/RTD/20200212_HV_RTD.csv", header = TRUE, sep = ",")
HV_20200212_25 <- RTD(HV_20200212_25)

HV_20200211_14 <- read.csv("../data/RTD/20200211_HV_RTD.csv", header = TRUE, sep = ",")
HV_20200211_14 <- RTD(HV_20200211_14)

HV_20200219_14 <- read.csv("../data/RTD/20200219_HV_RTD.csv", header = TRUE, sep = ",")
HV_20200219_14 <- RTD(HV_20200219_14)

HV_20201115_25_A <- read.csv("../data/RTD/20201115A_HV_RTD.csv", header = TRUE, sep = ",")
HV_20201115_25_A <- RTD(HV_20201115_25_A)

HV_20201115_25_B <- read.csv("../data/RTD/20201115B_HV_RTD.csv", header = TRUE, sep = ",")
HV_20201115_25_B <- RTD(HV_20201115_25_B)

HV_20201115_25_C <- read.csv("../data/RTD/20201115C_HV_RTD.csv", header = TRUE, sep = ",")
HV_20201115_25_C <- RTD(HV_20201115_25_C)



Total <- data.frame(HV_20200211_14$Time)
colnames(Total) <- ("Time")
Total$HV_14 <- (HV_20200211_14$E + HV_20200219_14$E)/2
Total$HV_25 <- (HV_20200212_25$E + HV_20200218_25$E+ HV_20201115_25_A$E + HV_20201115_25_B$E)/4
Total$NV_14 <- (NV_20200211_14$E + NV_20200219_14$E)/2
Total$NV_25 <- (NV_20200212_25$E + NV_20200218_25$E)/2

```


#qualitative F(t) comparisons
```{r}
F_25 <- ggplot(HV_20201115_25_A, aes(x=Time, y = f))+
  geom_line()+
  geom_line(data = HV_20201115_25_B, mapping = aes(x = Time, y = f))+
  geom_line(data = NV_20200212_25, mapping = aes(x= Time, y = f), col = "red")+
  geom_line(data = NV_20200218_25, mapping = aes(x= Time, y = f), col = "red")

F_25

F_HV <- ggplot(HV_20201115_25_A, aes(x=Time, y = f))+
  geom_line()+
  geom_line(data = HV_20201115_25_B, mapping = aes(x = Time, y = f))+
  geom_line(data = HV_20200211_14, mapping = aes(x= Time, y = f), col = "red")+
  geom_line(data = HV_20200219_14, mapping = aes(x= Time, y = f), col = "red")

F_HV
              
```


#qualitative replicate comparison

```{r}

#Added weird aes as a test of legends
NV_25 <- ggplot(NV_20200212_25, aes(x =Time, y = E))+
  geom_line(mapping = aes(linetype = 'replicate', color = 'replicate'))+
  geom_line(data = NV_20200218_25, mapping = aes(x = Time, y = E, linetype = 'replicate', color = 'replicate'))+
  geom_line(data = Total, mapping = aes(x = Time, y = NV_25, linetype = 'average', color = 'average'))+
  xlab("t")+
  ylab("E(t)")+
  scale_colour_manual(name = 'color', values =c('replicate'='black','average'='red'), labels = c('Average','Replicate'))
  scale_linetype_manual(name = 'linetype', values = c('replicate' = 'dashed', 'average' ='solid'), labels = c('Average', 'Replicate'))

NV_25

NV_14 <- ggplot(NV_20200211_14, aes(x = Time, y = E))+
  geom_line()+
  geom_line(data = NV_20200219_14, mapping = aes(x = Time, y = E))+
  geom_line(data = Total, mapping = aes(x = Time, y = NV_14), col = "red")+
  xlab("t")+
  ylab("E(t)")

HV_25 <- ggplot(HV_20200212_25, aes(x = Time, y = E))+
  geom_line()+
  geom_line(data = HV_20200218_25, mapping = aes(x = Time, y = E))+
  geom_line(data = HV_20201115_25_A, mapping = aes(x = Time, y= E), cex = 2)+
  geom_line(data = HV_20201115_25_B, mapping = aes(x = Time, y= E), cex = 2)+
  #geom_line(data = HV_20201115_25_C, mapping = aes(x = Time, y= E), cex = 2)+
  geom_line(data = Total, mapping = aes(x = Time, y = HV_25), col = "red", cex = 2)+
  xlab("t")+
  ylab("E(t)")

HV_25

HV_14 <- ggplot(HV_20200211_14, aes(x = Time, y = E))+
  geom_line()+
  geom_line(data = HV_20200219_14, mapping = aes(x = Time, y = E))+
  geom_line(data = Total, mapping = aes(x = Time, y = HV_14), col = "red")+
  xlab("t")+
  ylab("E(t)")

ggarrange(NV_25, NV_14, HV_25, HV_14, labels = c("NV25", "NV14", "HV25", "HV14"), ncol = 2, nrow = 2)
ggsave("../output/Replication.pdf")
ggsave("../output/Replication.png")


#Concentrations
HV_25_raw <- ggplot(HV_20200212_25, aes(x = Time, y = Conc))+
  geom_line()+
  geom_line(data = HV_20200218_25, mapping = aes(x = Time, y = Conc))+
  geom_line(data = HV_20201115_25_A, mapping = aes(x = Time, y= Conc), cex = 1.5)+
  geom_line(data = HV_20201115_25_B, mapping = aes(x = Time, y= Conc), cex = 1.5)+
  geom_line(data = HV_20201115_25_C, mapping = aes(x = Time, y= Conc), cex = 1.5)+
  xlab("t")+
  ylab("Cells/mL")

HV_25_raw

```

```{r}

#Added weird aes as a test of legends
NV_25 <- ggplot(NV_20200212_25, aes(x =Time, y = CDF))+
  geom_line()+
  geom_line(data = NV_20200218_25, mapping = aes(x = Time, y = CDF))+
  xlab("t")+
  ylab("F(t)")

NV_25

NV_14 <- ggplot(NV_20200211_14, aes(x = Time, y = CDF))+
  geom_line()+
  geom_line(data = NV_20200219_14, mapping = aes(x = Time, y = CDF))+
  xlab("t")+
  ylab("F(t)")

HV_25 <- ggplot(HV_20200212_25, aes(x = Time, y = CDF))+
  geom_line()+
  geom_line(data = HV_20200218_25, mapping = aes(x = Time, y = CDF))+
  xlab("t")+
  ylab("F(t)")

HV_14 <- ggplot(HV_20200211_14, aes(x = Time, y = CDF))+
  geom_line()+
  geom_line(data = HV_20200219_14, mapping = aes(x = Time, y = CDF))+
  xlab("t")+
  ylab("F(t)")

ggarrange(NV_25, NV_14, HV_25, HV_14, labels = c("NV25", "NV14", "HV25", "HV14"), ncol = 2, nrow = 2)
ggsave("../output/Replication_CDF.pdf")
ggsave("../output/Replication_CDF.png")


```

#qualitative RT comparison within villi treatments
```{r}

#NV (blue is 14, black is 25)
NV <- ggplot(NV_20200218_25, aes(x = Time, y = E))+
  geom_point(size=2,alpha=0.6)+
  geom_line()+
  geom_point(data = NV_20200212_25, mapping = aes(x = Time, y = E), size =2, alpha = 0.6)+
  geom_point(data = NV_20200211_14, mapping = aes(x = Time, y = E), size =2, alpha = 0.6, col = "red")+
  geom_point(data = NV_20200219_14, mapping = aes(x = Time, y = E), size = 2, alpha = 0.6, col = "red")+
  xlab("t") +
  #Peak
  geom_vline(xintercept = 3, col = "green")+
  geom_vline(xintercept = mean(c(NV_20200218_25$Time[NV_20200218_25$E == max(NV_20200218_25$E)],
                                 NV_20200212_25$Time[NV_20200212_25$E == max(NV_20200212_25$E)])))+
  geom_vline(xintercept = mean(c(NV_20200211_14$Time[NV_20200211_14$E == max(NV_20200211_14$E)],
                                 NV_20200219_14$Time[NV_20200219_14$E == max(NV_20200219_14$E)col = "red")+
  #Median
  geom_vline(xintercept = mean(c(11.799, 10.177)), size = 1.5)+
  geom_vline(xintercept = mean(c(7.982, 9.507)), size = 1.5, col = "red")+
  ylab("E(t)")

NV

ggsave("../output/NV_RT.pdf")
ggsave("../output/NV_RT.png")

#HV (blue is 14, black is 25)
HV <- ggplot(HV_20200218_25, aes(x = Time, y = E))+
  geom_point(size=2,alpha=0.6)+
  geom_point(data = HV_20200212_25, mapping = aes(x = Time, y = E), size =2, alpha = 0.6)+
  geom_point(data = HV_20200211_14, mapping = aes(x = Time, y = E), size =2, alpha = 0.6, col = "blue")+
  geom_point(data = HV_20200219_14, mapping = aes(x = Time, y = E), size = 2, alpha = 0.6, col = "blue")+
  #Peak
  geom_vline(xintercept = mean(c(HV_20200218_25$Time[HV_20200218_25$E == max(HV_20200218_25$E)],
        HV_20200212_25$Time[HV_20200212_25$E == max(HV_20200212_25$E)])), size = 1.5, linetype = "dashed")+
  geom_vline(xintercept = mean(c(HV_20200211_14$Time[HV_20200211_14$E == max(HV_20200211_14$E)],
        HV_20200219_14$Time[HV_20200219_14$E == max(HV_20200219_14$E)])),col = "red", size = 1.5, linetype = "dashed")+
  #Median
  geom_vline(xintercept = mean(c(9.456, 9.507)), size = 1.5)+
  geom_vline(xintercept = mean(c(9.125, 7.548)), size = 1.5, col = "red")+
  xlab("t") +
  ylab("E(t)")

ggarrange(NV, HV, labels = c("NV", "HV"), ncol = 1, nrow = 2)
ggsave("../output/RT.pdf")
ggsave("../output/RT.png")
```

#qualitative V comparison within RT treatments
```{r}
#25 (blue is NV, black is HV)
RT_25 <- ggplot(HV_20200218_25, aes(x = Time, y = E))+
  geom_point(size=2,alpha=0.6)+
  geom_point(data = HV_20200212_25, mapping = aes(x = Time, y = E), size =2, alpha = 0.6)+
  geom_point(data = NV_20200218_25, mapping = aes(x = Time, y= E), size = 2, alpha = 0.6, col = "blue")+
  geom_point(data = NV_20200212_25, mapping = aes(x = Time, y = E), size = 2, alpha = 0.6, col = "blue")+
  xlab("t")+
  ylab("E(t)")

#14 (blue is NV, black is HV)
RT_14 <- ggplot(HV_20200211_14, aes(x = Time, y = E))+
  geom_point(size=2,alpha=0.6)+
  geom_point(data = HV_20200219_14, mapping = aes(x = Time, y = E), size =2, alpha = 0.6)+
  geom_point(data = NV_20200211_14, mapping = aes(x = Time, y= E), size = 2, alpha = 0.6, col = "blue")+
  geom_point(data = NV_20200219_14, mapping = aes(x = Time, y = E), size = 2, alpha = 0.6, col = "blue")+
  xlab("t")+
  ylab("E(t)")

ggarrange(RT_25, RT_14, labels = c("25", "14"), ncol = 1, nrow = 2)
ggsave("../output/V.pdf")
ggsave("../output/V.png")


```

#Median and Peak comparison
#red is NV, black is HV, dashed is 25, solid is 14
```{r}

Median <- ggplot(HV_20200218_25, aes(x = Time, y = E))+ 
  geom_line(linetype = "dashed", size = 0.5)+
  geom_line(data = HV_20200212_25, mapping = aes(x = Time, y = E), size = 0.5, linetype = "dashed")+
  geom_line(data = NV_20200218_25, mapping = aes(x = Time, y = E), size = 0.5, col = "red", linetype = "dashed")+
  geom_line(data = NV_20200212_25, mapping = aes(x = Time, y = E), size = 0.5, col = "red", linetype = "dashed")+
  geom_line(data = HV_20200211_14, mapping = aes(x = Time, y = E), size = 0.5)+
  geom_line(data = HV_20200219_14, mapping = aes(x = Time, y = E), size = 0.5)+
  geom_line(data = NV_20200211_14, mapping = aes(x = Time, y = E), col = "red", size = 0.5)+
  geom_line(data = NV_20200219_14, mapping = aes(x = Time, y = E), col = "red", size = 0.5)+
  xlab("t (mins)")+
  ylab("E(t)")+
  geom_vline(xintercept = mean(c(9.507,9.456)), size = 1.5, linetype = "dashed")+
  geom_vline(xintercept = mean(c(11.799, 10.177)), size = 1.5, col = "red", linetype = "dashed")+
  geom_vline(xintercept = mean(c(9.125, 7.548)), size = 1.5)+
  geom_vline(xintercept = mean(c(7.982, 9.507)), size = 1.5, col = "red")


Median

ggsave("../output/Median.pdf")
ggsave("../output/Median.png")

Peak <- ggplot(HV_20200211_14, aes(x = Time, y = E))+
  geom_line(size = 0.5)+
  geom_line(data = HV_20200218_25, mapping = aes(x = Time, y = E), size = 0.5, linetype = "dashed")+
  geom_line(data = HV_20200212_25, mapping = aes(x = Time, y = E), size = 0.5, linetype = "dashed")+
  geom_line(data = NV_20200218_25, mapping = aes(x = Time, y = E), size = 0.5, col = "red", linetype = "dashed")+
  geom_line(data = NV_20200212_25, mapping = aes(x = Time, y = E), size = 0.5, col = "red", linetype = "dashed")+
  geom_line(data = HV_20200219_14, mapping = aes(x = Time, y = E), size = 0.5)+
  geom_line(data = NV_20200211_14, mapping = aes(x = Time, y = E), col = "red", size = 0.5)+
  geom_line(data = NV_20200219_14, mapping = aes(x = Time, y = E), col = "red", size = 0.5)+
  xlab("t (mins)")+
  ylab("E(t)")+
  geom_vline(xintercept = mean(c(HV_20200218_25$Time[HV_20200218_25$E == max(HV_20200218_25$E)],
                                 HV_20200212_25$Time[HV_20200212_25$E == max(HV_20200212_25$E)])), size = 1.5, linetype = "dashed")+
  geom_vline(xintercept = mean(c(NV_20200218_25$Time[NV_20200218_25$E == max(NV_20200218_25$E)],
                                 NV_20200212_25$Time[NV_20200212_25$E == max(NV_20200212_25$E)])),col = "red", size = 1.5, linetype = "dashed")+
  geom_vline(xintercept = mean(c(HV_20200211_14$Time[HV_20200211_14$E == max(HV_20200211_14$E)],
                                 HV_20200219_14$Time[HV_20200219_14$E == max(HV_20200219_14$E)])), size = 3)+
  geom_vline(xintercept = mean(c(NV_20200211_14$Time[NV_20200211_14$E == max(NV_20200211_14$E)],
                                 NV_20200219_14$Time[NV_20200219_14$E == max(NV_20200219_14$E)])),col = "red", size = 1)

Peak

ggsave("../output/Peak.pdf")
ggsave("../output/Peak.png")

ggarrange(Median, Peak, ncol = 2, nrow = 1)
ggsave("../output/Median_peak.pdf", width = 20, height = 10)
ggsave("../output/Median_peak.png", width = 20, height = 10)
```


#Median and Peak comparison
#red is NV, black is HV, dashed is 25, solid is 14
```{r}
Median_avg <- ggplot(Total, aes(x = Time, y = HV_25))+ 
  geom_line(mapping = aes(linetype = "RT_25", color = "HV"), size = 0.5)+
  geom_line(data = Total, mapping = aes(x = Time, y = NV_25, color = "NV", linetype = "RT_25"), size = 0.5)+
  geom_line(data = Total, mapping = aes(x = Time, y = HV_14, color = "HV", linetype = "RT_14"), size = 0.5)+
  geom_line(data = Total, mapping = aes(x = Time, y = NV_14, color = "NV", linetype = "RT_14"), size = 0.5)+
  xlab("t (mins)")+
  ylab("E(t)")+
  geom_vline(aes(xintercept = mean(c(9.507,9.456))), size = 1.5, col = "black", linetype = "dashed")+
  geom_vline(aes(xintercept = mean(c(11.799, 10.177))), size = 1.5, col = "red", linetype = "dashed")+
  geom_vline(aes(xintercept = mean(c(9.125, 7.548))), size = 1.5, col = "black", linetype = "solid")+
  geom_vline(aes(xintercept = mean(c(7.982, 9.507))), size = 1.5, col = "red", linetype = "solid")+
  scale_color_manual(name = " # villi", labels = c('0 villi','296 villi'),values =c('HV'='black','NV'='red'))+
  scale_linetype_manual(name = expression(paste(tau)), values = c('RT_25' = 'dashed', 'RT_14' ='solid'), labels = c("14 minutes","25 minutes"))+
  guides(color = guide_legend(override.aes = list(linetype=c(1,1), size = c(5,5))))


Median_avg

ggsave("../output/Median_avg.pdf", dpi = 400)
ggsave("../output/Median_avg.png", dpi = 400)

Peak_avg <- ggplot(Total, aes(x = Time, y = HV_25))+ 
  geom_line(mapping = aes(linetype = "RT_25", color = "HV"), size = 0.5)+
  geom_line(data = Total, mapping = aes(x = Time, y = NV_25, color = "NV", linetype = "RT_25"), size = 0.5)+
  geom_line(data = Total, mapping = aes(x = Time, y = HV_14, color = "HV", linetype = "RT_14"), size = 0.5)+
  geom_line(data = Total, mapping = aes(x = Time, y = NV_14, color = "NV", linetype = "RT_14"), size = 0.5)+
  xlab("t (mins)")+
  ylab("E(t)")+
  geom_vline(xintercept = mean(c(HV_20200218_25$Time[HV_20200218_25$E == max(HV_20200218_25$E)],
                                 HV_20200212_25$Time[HV_20200212_25$E == max(HV_20200212_25$E)])),col = "black", size = 1.5, linetype = "dashed")+
  geom_vline(xintercept = mean(c(NV_20200218_25$Time[NV_20200218_25$E == max(NV_20200218_25$E)],
                                 NV_20200212_25$Time[NV_20200212_25$E == max(NV_20200212_25$E)])),col = "red", size = 1.5, linetype = "dashed")+
  geom_vline(xintercept = mean(c(HV_20200211_14$Time[HV_20200211_14$E == max(HV_20200211_14$E)],
                                 HV_20200219_14$Time[HV_20200219_14$E == max(HV_20200219_14$E)])), col = "black", size = 3, linetype = "solid")+
  geom_vline(xintercept = mean(c(NV_20200211_14$Time[NV_20200211_14$E == max(NV_20200211_14$E)],
                                 NV_20200219_14$Time[NV_20200219_14$E == max(NV_20200219_14$E)])), col = "red", size = 1, linetype = "solid")+
  scale_color_manual(name = " # villi", labels = c('0 villi','296 villi'),values =c('HV'='black','NV'='red'))+
  scale_linetype_manual(name = expression(paste(tau)), values = c('RT_25' = 'dashed', 'RT_14' ='solid'), labels = c("14 minutes","25 minutes"))+
  guides(color = guide_legend(override.aes = list(linetype=c(1,1), size = c(5,5))))

Peak_avg

ggsave("../output/Peak_avg.pdf", dpi = 400)
ggsave("../output/Peak_avg.png", dpi = 400)

ggarrange(Median_avg, Peak_avg, ncol = 2, nrow = 1)
ggsave("../output/Median_peak_avg.pdf", width = 30, height = 10)
ggsave("../output/Median_peak_avg.png", width = 30, height = 10)
```
```{r}
RT_25 <- ggplot(Total, aes(x = Time, y = HV_25, fill = "HV"))+
  geom_bar(inherit.aes = TRUE, stat = "identity", col = "white")+
  geom_bar(data = Total, mapping = aes(x = Time, y = NV_25, fill = "NV"), stat = "identity", col = "white")+
  xlab("t (mins)")+
  ylab("E(t)")+
  scale_fill_manual(name = " # villi", labels = c('0 villi','296 villi'),values = c('NV' = adjustcolor( "red", alpha.f = 0.2), 'HV' =adjustcolor( "black", alpha.f = 0.2)))+
  theme(plot.margin = unit(c(0,0,0,0), "lines"))+
  geom_vline(aes(xintercept = mean(c(9.507,9.456))), size = 1, col = "black")+
  geom_vline(aes(xintercept = mean(c(11.799, 10.177))), size = 1, col = "red")+
  ggtitle(expression(paste(tau, " = 25 minutes")))

RT_25
ggsave("../output/RT_25_bins.png",width = 10, height = 3.25)
ggsave("../output/RT_25_bins.pdf",width = 10, height = 3.25)

RT_14 <- ggplot(Total, aes(x = Time, y = HV_14, fill = "HV"))+
  geom_bar(inherit.aes = TRUE, stat = "identity", col = "white")+
  geom_bar(data = Total, mapping = aes(x = Time, y = NV_14, fill = "NV"), stat = "identity", col = "white")+
  xlab("")+
  ylab("E(t)")+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), plot.margin = unit(c(0,0,0,0), "lines"))+
  scale_fill_manual(name = " # villi", labels = c('0 villi','296 villi'),values = c('NV' = adjustcolor( "red", alpha.f = 0.2), 'HV' =adjustcolor( "black", alpha.f = 0.2)))+
  geom_vline(aes(xintercept = mean(c(9.125, 7.548))), size = 1, col = "black")+
  geom_vline(aes(xintercept = mean(c(7.982, 9.507))), size = 1, col = "red")+
  ggtitle(expression(paste(tau, " = 14 minutes \n Proportion of particles exiting bioreactor")))
  
RT_14
ggsave("../output/RT_14_bins.png",width = 10, height = 3)
ggsave("../output/RT_14_bins.pdf",width = 10, height = 3)

ggarrange(RT_14, RT_25, nrow = 2, ncol = 1, heights = c(1, 1), common.legend = TRUE)
ggsave("../output/bins.png")
```
```

