---
title: "Vill size distribution"
author: "Jay T. Lennon"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes:
   - \usepackage{array}
output: pdf_document
geometry: margin=2.54cm
---

# Overview
Data from Murray et al. (2017) Gastroenterology (2017)152:787–798.e2. https://www.ncbi.nlm.nih.gov/pubmed/27864127 looking 1,345 patients with range of Celiac's disease. 
Data not available in original paper, but Jack Syage from Immunogenex sent excel files. 
Goal is to look at distribution of villi height to crypt depth where smaller values are symptomatic of disease.

# Set working directory and load packages
```{r}
rm(list = ls())
getwd()
setwd("~/GitHub/Gut")
require("bbmle")
require("grid")
require("png")
```

# Load data
```{r}
# load raw data
getwd()
setwd("~/GitHub/Gut")
data <- read.table("data/villi.celiac.separated.txt", sep = "\t", header = TRUE)
vh.cd <- na.omit(data$AVEVH_CD_Corrected)
vh <- na.omit(data$AVEVH_Corrected)
cd <- na.omit(data$AVECD_Corrected)
```

# Make villi height figure
```{r}
png(filename="~/GitHub/Gut/output/villiheight.distribution.png",
     width = 900, height = 900, res = 96*2)

# create histogram
hist <- hist(vh, breaks = 50, col = "grey", las = 1, 
             xlab = "Villi height (mm)", main = NA, freq = F)

# add kernel density
lines(density(vh, adjust = 2), col = "red", lwd = 1.5)

dev.off()
graphics.off()

img <- readPNG("~/GitHub/Gut/output/villiheight.distribution.png")
grid.raster(img)
```
# Make crypt depth figure
```{r}
png(filename="~/GitHub/Gut/output/cryptdepth.distribution.png",
     width = 900, height = 900, res = 96*2)

# create histogram
hist <- hist(cd, breaks = 50, col = "grey", las = 1, 
             xlab = "Crypt depth (mm)", main = NA, freq = F)

# add kernel density
lines(density(cd, adjust = 2), col = "red", lwd = 1.5)

dev.off()
graphics.off()

img <- readPNG("~/GitHub/Gut/output/cryptdepth.distribution.png")
grid.raster(img)
```
# Make crypt depth figure
```{r}
png(filename="~/GitHub/Gut/output/villi.distribution.png",
     width = 900, height = 900, res = 96*2)

# create histogram
hist <- hist(vh.cd, breaks = 50, col = "grey", las = 1, 
             xlab = "Villi heigh : Crypt depth", main = NA, freq = F)

# add kernel density
lines(density(vh.cd, adjust = 2), col = "red", lwd = 1.5)

dev.off()
graphics.off()

img <- readPNG("~/GitHub/Gut/output/villi.distribution.png")
grid.raster(img)
```

